A Blockchain Consensus Protocol With\\Horizontal Scalability

### 2017-08-27 paper/s5-evaluation.tex
Fix paper

\begin{figure*}[t]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\linewidth]{neighbour-fixed/throughput-vs-population}
    \caption{Every node make transactions with a fixed node.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\linewidth]{neighbour-random/throughput-vs-population}
    \caption{Every node make transactions with a random node.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput increases as the population increases when every node transact at the same rate.
  Making transactions with fixed nodes results in a higher throughput because of the caching mechanism.}
  \label{fig:global-throughput}
\end{figure*}

The prototype implementation can be found on GitHub.
\begin{displayquote}
\url{https://github.com/kc1212/checo}
\end{displayquote}
It implements the three protocols and the Extended TrustChain.
We also implement the caching optimisation discussed in \Cref{sec:caching}.
It is written in the Python programming language\footnote{\url{https://www.python.org/}}.
The cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.
Both of which are provided by libnacl~\footnote{\url{https://pypi.python.org/pypi/libnacl}}.

@@

For~\Cref{fig:global-throughput-fixed},
the magnitude of our throughput may not be self-evident at first glance.
Recall that we fixed the transaction rate to 2 TPS,
but how is it possible to have around 4800 transactions per second for 1200 nodes (which is 4 TX/s)?
This is due to the way validated transactions are calculated.
Transactions are between two parties, hence if every node makes two transactions per second,
every node also expects to receive two transactions per second.
Hence, for every node, the TX blocks are created at 4 per second.
Validation requests are sent at the same rate, which explains the magnitude.

Overall, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.
For more experimental results refer to~\cite[Chapter 5]{checo}???.

>>>>

\begin{figure*}[ht]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\linewidth]{neighbour-fixed/throughput-vs-population}
    \caption{Every node make transactions with a fixed node.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\linewidth]{neighbour-random/throughput-vs-population}
    \caption{Every node make transactions with a random node.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput increases as the population increases when every node transact at the same rate.
  Making transactions with fixed nodes results in a higher throughput because of the caching mechanism.}
  \label{fig:global-throughput}
\end{figure*}

A free and open source implementation can be found on GitHub: \url{https://github.com/kc1212/checo}.
It implements the three protocols and the Extended TrustChain.
We also implement the caching optimisation discussed in \Cref{sec:caching}.
It is written in the Python programming language.
The cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.

@@

For~\Cref{fig:global-throughput-fixed},
the magnitude of our throughput may not be self-evident at first glance.
Recall that we fixed the transaction rate to 2 TPS,
but how is it possible to have around 4800 transactions per second for 1200 nodes (which is 4 TX/s)?
This is due to the way validated transactions are calculated.
Transactions are between two parties, hence if every node makes two transactions per second,
every node also expects to receive two transactions per second.
Hence, for every node, the TX blocks are created at 4 per second.
Validation requests are sent at the same rate, which explains the magnitude.
Overall, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.

The communication complexity of the consensus protocol grows polynomially as the number of facilitators grows linearly.
Hence, the consensus protocol will take longer to complete and larger fragments must be sent for transaction verification.
The result is that transactions verification will take longer.
On the other hand, it does not significantly impact the throughput.
We refer the reader to~\cite[Chapter 5]{checo} for additional analysis of the effect of the number of facilitators as well as other experimental results.

### 2017-08-27 presentation/presentation.tex
Fix paper

\title{Blockchain Consensus Protocol with\\Horizontal Scalability}
% \subtitle{Optional Subtitle}

@@

\begin{frame}{The dangers of centralisation:~Examples}
  \begin{itemize}
    \item Facebook can predict your opinions and desires better than your spouse~\cite{youyou2015computer}
    \item With intimate knowledge of the individuals,
      Facebook creates ``psychographic'' profiles in political campaigns~\cite{psychographic}
    \item Baidu's promoted search result on experimental medical care caused death of a student~\cite{weizexi}
  \end{itemize}
  \note{
    \begin{itemize}
      \item The student had cancer---(synovial sarcoma)
      \item The treatment was phased out at clinical stage in the US because the success rate is too low
      \item ``The study was conducted on 86,220 volunteers who have a Facebook account and who
      completed a hundred-item personality questionnaire. The Facebook algorithm predicted the volunteers'
      answers based on monitoring their Facebook Likes – which webpages, images and clips they tagged with the
      Like button. The more Likes, the more accurate the predictions. The algorithm's predictions were compared
      with those of work colleagues, friends, family members and spouses. Amazingly, the algorithm needed a set
      of only ten Likes in order to outperform the predictions of work colleagues. It needed seventy Likes to
      outperform friends, 150 Likes to outperform family members and 300 Likes to outperform spouses. In other
      words, if you happen to have clicked 300 Likes on your Facebook account, the Facebook algorithm can
      predict your opinions and desires better than your husband or wife!'' -Harari, \emph{Homo Deus}
      \item Summary: we live in an age where companies and governments are able to control our thoughts,
      where is the freedom and liberty in that?
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{Blockchain:~not there yet}
  \begin{itemize}
    \item Consensus algorithm of early blockchain systems do not scale
    \item Bitcoin (PoW) is limited to 7 transactions per second
    \item 100,000 transaction backlog in May 2017
    \item We require horizontal scalability for ubiquitous use
    \item More nodes = better performance and throughput
  \end{itemize}
\end{frame}

@@

\begin{frame}{Related work}
  State-of-the-art: Sharding
  \begin{itemize}
  \item Split state into multiple shards
  \item Shards run consensus algorithm in parallel
  \item Difficult to perform atomic inter-shard transactions
    \begin{itemize}
      \item Elastico: not possible
      \item OmniLedger: via Atomic Commit protocol
    \end{itemize}
  \item Additional complexity
  \item Diminishing return
  \end{itemize}
\end{frame}

>>>>

\title{A Blockchain Consensus Protocol With\\Horizontal Scalability}
% \subtitle{Optional Subtitle}

@@

\begin{frame}{The dangers of centralisation:~Examples}
  \begin{itemize}
    \item Facebook can predict your opinions and desires better than your spouse~\cite{youyou2015computer}
    \item With intimate knowledge of the individuals,
      Facebook creates ``psychographic'' profiles in political campaigns~\cite{psychographic}
    \item Baidu's promoted search result on medical care caused death of a student~\cite{weizexi}
  \end{itemize}
  \note{
    \begin{itemize}
      \item The student had cancer---(synovial sarcoma)
      \item The treatment was phased out at clinical stage in the US because the success rate is too low
      \item ``The study was conducted on 86,220 volunteers who have a Facebook account and who
      completed a hundred-item personality questionnaire. The Facebook algorithm predicted the volunteers'
      answers based on monitoring their Facebook Likes – which webpages, images and clips they tagged with the
      Like button. The more Likes, the more accurate the predictions. The algorithm's predictions were compared
      with those of work colleagues, friends, family members and spouses. Amazingly, the algorithm needed a set
      of only ten Likes in order to outperform the predictions of work colleagues. It needed seventy Likes to
      outperform friends, 150 Likes to outperform family members and 300 Likes to outperform spouses. In other
      words, if you happen to have clicked 300 Likes on your Facebook account, the Facebook algorithm can
      predict your opinions and desires better than your husband or wife!'' -Harari, \emph{Homo Deus}
      \item Summary: we live in an age where companies and governments are able to control our thoughts,
      where is the freedom and liberty in that?
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{Blockchain:~not there yet}
  \begin{itemize}
    \item Consensus algorithm of early blockchain systems do not scale
    \item Bitcoin (PoW) is limited to 7 transactions per second
    \item 100,000 transaction backlog in May 2017
    \item We require horizontal scalability for ubiquitous use
    \item More nodes = better transaction throughput
  \end{itemize}
\end{frame}

@@

% \begin{frame}{Related work}
%   State-of-the-art: Sharding
%   \begin{itemize}
%   \item Split state into multiple shards
%   \item Shards run consensus algorithm in parallel
%   \item Difficult to perform atomic inter-shard transactions
%     \begin{itemize}
%       \item Elastico: not possible
%       \item OmniLedger: via Atomic Commit protocol
%     \end{itemize}
%   \item Additional complexity
%   \item Diminishing return
%   \end{itemize}
% \end{frame}
